Broom: Safe Region-Based Memory Management for Dataflow Programs

### 2015-10-21 paper/type-system.tex
Touch techrep.
Reduced rules to use in main paper.

\input{fb-syntax}
\input{fb-auxdef}
\input{fb-staticsem}
\input{fb-morewfrules}

@@

The expression language has been equipped with lambda abstraction
($\lambdaexp{...}{\xbar : \taubar}{e}$) and application ($e(\bar{e})$)
expressions to define and apply anonymous functions. These expressions
are uncurried variants of the corresponding expressions from System F.
Note that FGJ formalism does not include higher-order functions, hence
the syntactic class (\C{T}) of FGJ types needs to be extended with an
(uncurried) arrow type.

@@

>>>>

\input{fb-syntax}

@@

The expression language has been equipped with lambda abstraction
($\lambdaexp{...}{\xbar : \taubar}{e}$) and application ($e(\bar{e})$)
expressions to define and apply anonymous functions. Module the angle
braces (whose presence will be justified later), these expressions are
uncurried variants of the corresponding expressions from System F.
Note that FGJ formalism does not include higher-order functions, hence
the syntactic class (\C{T}) of FGJ types needs to be extended with an
(uncurried) arrow type.

@@

\input{fb-staticsem}
\subsection{Types and Well-formedness}

Static semantics of \fbname is defined by the rules to establish
well-formedness of region types and region constraints, check
subtyping between a pair of region types, and type-check expressions
against region types. Fig.~\ref{fig:fb-staticsem} contains an
illustrative subset of such rules\footnote{The full formal development
can be found in our technical report~\cite{techrep}}, along with some
auxiliary definitions. The judgments defined by these rules make use
of a context ($\A$), which is a tuple of:
\begin{itemize}
\item A set ($\rhoenv \in 2^\rgn$) of static identifiers of regions
that are estimated to be live,
\item A finite map ($\aenv \in \tyvar \mapsto \fgjN$) of type
variables to their bounds\footnote{A bound of a type variable in
FGJ~\cite{fgj} is the class that type variable was declared to extend.
The map from type variables to their bounds is denoted as $\Delta$
in FGJ formalism}.
\item A constraint formula ($\phicx$) that captures the outlives
constraints on regions in $\rhoenv$.
\end{itemize}
